A note on observation processes in epidemic models

### 2019-11-27 ms/ms.tex
more stuff
.

Note that incidence (the number of \emph{newly} infected individuals) is different from 
prevalence (the number of \emph{currently} infected individuals) \citep{bjornstad2018epidemics}:
the observed dynamics of incidence depend on the reporting time step (because the sum of 
true incidence is equal to the final size of an epidemic), whereas those of
prevalence do not.
While they are relatively
uncommon, some models do not make a clear distinction between prevalence and 
incidence 
\citep{capistran2009parameter, hooker2010parameterizing, yang2013stability, gonzalez2014fractional}.

@@

We thank David Earn for providing useful comments.

>>>>

We emphasize that incidence (i.e., the number of \emph{newly} infected individuals) is different from prevalence (i.e., the number of \emph{currently} infected individuals) \citep{bjornstad2018epidemics}.
The dynamics of incidence depend on the reporting time step (because the sum of true incidence is equal to the final size of an epidemic), whereas those of prevalence do not.
We expect the dynamics of incidence and prevalence to be similar only when the reporting time step is similar to the disease generation time \citep{fine1982measles}.
While they are uncommon, some models do not make a clear distinction between prevalence and 
incidence \citep{capistran2009parameter, hooker2010parameterizing, yang2013stability, gonzalez2014fractional}.

@@

We thank David Earn for providing helpful comments on the manuscript. BMB is supported by an NSERC Discovery grant.
